Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-08-20 writeup/RochatEtal_ResponseToReviewers.tex

  \item {\it First of all, generation mechanism of submesoscale inertial-gravity waves in summer
        and early fall is unclear to me. In the paper, authors attribute the mechanism to
        internal tides (X-12, section 6, last sentence) and emphasize using the tidal forcing in
        their model (X-5, section 2, 2nd paragraph). However, authors do not explain or show
        any interaction mechanism of internal tides (please at least add some reference). With
        the fixed frequencies of tidal constituents and existence of the critical latitude for the
        diurnal tides, I am not sure what mechanism can represent the surface near-inertial
        wave generation within the whole analyzed region by internal tides (with the
        horizontal scales of 10-100km). If authors compare Figures 2 and 4 with those
        estimated from the non-tidal forcing run in the Supplemental material, authors'
        conclusion could be strengthened.}\\

        \bdp
          The generation mechanism generation of internal
          waves are changes in the wind (NIWs) and barotropic tides sloshing over
          topographic features --- we are not claiming that there exists a different
          generation mechanism
          in summer compared to winter; neither are we claiming that surface NIWs
          are generated by internal tides. What is different is the near-surface
          expression of IGWs, which is very sensitive to the near-surface stratification
          (D'saro 1978). This is particular true for higher vertical-mode waves
          (supplemental material).\\

          To reference potential mechanisms of how energy can quickly be transferred to
          high wavenumbers by interaction with mesoscale-submesoscale turbulence and
           PSI,  we added new references to the discussion (Ponte \& Klein 2015;
          Mackinon \& Winters 2004; Alford et al 2016). \\

          The simulation without tides (ECCO2 Adjoint) has much coarser
          horizontal resolution and barely resolves the submesoscales; its grid
          spacing is 18 km, while its effective resolution larger than 60 km.
      \edp

@@

        We thank  Christian Buckingham for the speedy and thorough review. Below we address
                  Buckingham's comments and suggestions.

\subsection{Major comments}

\begin{enumerate}

  \item {\it The authors must clearly demonstrate that increased inertia-gravity waves (IGWs) are
        responsible for the seasonal signal in horizontal divergence and SSH spectra at high
        wavenumbers. The authors argue that this is so but it is not demonstrated with sufficient
        clarity. It is true that a portion of this energy/variance will be attributed to internal waves
        modified by rotation but other flows give rise to divergence (and thus, SSH variance). Thus,
        the seasonal changes reported by the authors might be the result of seasonal changes in these
        other flows. Given that this is the main message of the paper, the authors must make this
        modification.}\\

        \bdp
            We have included wavenumber-frequency
            spectra of SSH variance (new figure 4) and KE (figure S7). Plotting bounds for the
            dispersion relationship of free IGWs, as suggested by the reviewer, unambiguously
            help us make that IGWs account for most of the super-inertial variability at
            scales between 10-100 km. Thanks for the excellent suggestion!
        \edp

@@

          Some investigators define mesoscales as flows with scales near the
          1st baroclinic deformation radius. But there is significant confusion
          owing to factors of  $2 \pi$ --- e.g., some investigators would use $R_1 = 30$ km,
          others would argue for $L_1 = 2\pi \times 30 \approx 190$ km
          (Wunsch \& Ferrari 2004; Ferrari \& Wunsch 2009).
          To add yet another controversy, Larichev \& Held 1995 argue
          that the deformation length is not the panacea as linear theorists
          suggest. In baroclinic geostrophic turbulence, the bulk of the
          energy production occurs on scales much larger than the deformation
          radius; the energy-containing scales of equilibrated baroclinic geostrophic
          turbulence are also larger than the deformation radius (e.g., Larichev \& Held 1995).\\

          According
          to our definition the mesoscales are the energy-containing scales of the
          flow --- the eddies that contain most of the eddy kinetic energy in the ocean
          (Ferrari \& Wunsch 2009). On observational
          grounds, this scale varies roughly from 100-300 km (from the centroid of KE wavenumber
          spectrum from current altimeters for example). We then \textit{define}
          the energetically subdominant scales, the scales smaller than about 100 km.
          Our lower wavelength definition is limited by the effective resolution
          of our higher resolution simulation ($\sim$10 km).
          This definition is consistent with Callies \& Ferrari 2013 (they did not
          define mesoscales/submesoscales based on scales that a sensor resolves
          as the reviewer suggests).\\

          We understand that our definition is imperfect --- we may amuse some readers but
          irritate others. But
          besides unsettled definitons by our community and consistency with our recent
          work (Rocha et al. 2016), there are at least two reasons for sticking to
          our definition: (i) this is the definition used by the SWOT community (Fu \& Ferrari
              2008); incidentally current altimeters do not resolve
              scales smaller then about 100 km; and (ii) our goal is to determine the flows
              (geostrophically balanced turbulence, inertia-gravity waves, etc) that
              dominate the 10-100 km horizontal
              scales and their seasonality. In any event,  readers that make to the first sentence of our
              abstract will find our explicit definition of submesoscales.
      \edp

@@

        \bdp
          We have added both nominal and effective resolutions.
        \edp

  \item {\it (Section 1, Paragraph 3) What types of horizontal and temporal scales for IGWs are
        we talking about here? How would this fall onto the Garrett-Munk (GM) internal
        wave spectrum? (Recall: the GM spectrum contains both balanced and unbalanced
        flows, not just internal waves, despite that the name suggests this.)}\\

        \bdp
          We explicit state that those are submesoscale IGWs. Using
          our definition of submesoscales are IGWs
          with horizontal scales about 10-100 km\footnote{Bill Young suggested the
          term submesoscale IGWs.}; IGWs have periods  The GM spectrum is not accurate
          close to the surface (most of our results concern surface currents and SSH,
          and it does not account for tidal and inertial peaks. We believe that the
          new plot of the wavenumber-frequency spectrum of the SSH
          variance (new Figure 4) --- following the reviewer's suggestion ---
          will more clearly convey the idea that there is no horizontal scale
          separation between submesoscale IGWs and submesoscale turbulence.\\

          If the reviewer is using ``balanced'' as a short to ``geostrophically
          balanced'', then the comment about the GM spectrum containing both balanced
          and unbalanced flows is incorrect.  GM used linear theory
          of IGW to synthesize observations, mostly mooring data --- they
          fitted an analytic model to (super-inertial) frequency spectra and
          different vertical modes (see Walter Munk's chapter
          in EPO 1981 and references therein).
          One could argue
          that other flows project onto similar temporal scales, but those motions
          are super-inertial (e.g., stratified turbulence), not (sub-inertial)
          balanced flows.
        \edp

### 2016-08-20 writeup/rocha_etal.tex
Small fixes

%
%
%\begin{figure*}[ht]
%  \begin{center}
%    \includegraphics[width=.65\textwidth]{figs/fig5.pdf}
% \caption{\small Surface (horizontal) kinetic energy (a) and sea-surface height variance wavenumber spectra (b)
% in the 1/48$^\circ$ simulation. Solid lines
% are spectra based on hourly snapshots, and dashed lines are spectra based on daily-averaged
% fields.}
% \label{fig5}
% \end{center}
%\end{figure*}
%
%
%Figure \ref{fig5}a depicts the horizontal wavenumber spectra of surface KE in
%April and October. At scales larger than 20 km, the April and October spectra based on hourly
%velocity snapshots (solid lines) are nearly indistinguishable from each other within 95$\%$ confidence level.
%Consistent with the results of
%\citet{rocha_etal2016}, who analyzed a 3-month output of the LLC4320 simulation in Drake Passage,
%there is significant high-frequency variabilty at submesoscales. Daily-averaging
%the velocity field suppresses spatial variability at scales smaller than about 250
%km, both in April and October (compare solid lines against dashed lines in Figure
%\ref{fig5}a). But this suppression is dramatic in October, when the IGWs peak. At scales
%smaller than 100 km, 39$\%$ of the surface KE in April is accounted for by super-inertial
%flows as opposed to 79$\%$ in October. The seasonality of subinertial submesoscale flows
%is strong, consistent
%with the results of \citet{sasaki_etal2014}, which are
%based on daily-averaged velocity fields of a different model without tidal forcing
%(P. Klein, personal communication).
%
%The IGWs project on the sea-surface.
%There is a dramatic difference between the spectra
%based on hourly and daily-averaged sea-surface height in October (Figure \ref{fig5}b): at scales smaller than 100 km, the spectra
%of hourly sea-surface height roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
%sea-surface height roughly follows a $-5$ power-law. At these scales, 33$\%$ of the sea-surface height variance in April is accounted for by super-inertial
%flows as opposed to 83$\%$ in October. Curiously, the out-of-phase seasonal cycle of submesoscale
%turbulence and near-surface submesoscale IGWs conspire to yield weak seasonality
%in the spectra of KE and sea-surface height variance based on hourly fields.
%
%
\section{Discussion and conclusion}
Our work adds to recent modeling \citep{sasaki_etal2014}
and observational \citep{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. In particular, our main finding is that in global simulations with embedded tides the
near-surface submesoscale IGWs in the Kuroshio Extension undergo
a strong seasonal cycle that is out of phase with the seasonal cycle of
submesoscale turbulence. IGW energy and SSH variance are significantly spread across
the submesoscales, likely through mesoscale refraction and dispersion \citep[e.g.,][and references there in]{ponte_klein2015,alford_etal2016}
 and parametric
subharmonic instability \citep[e.g., ][]{mackinnon_winters2005}. In the LLC simultions,
super-inertial IGWs account for most of the surface submesoscale KE and SSH variance;
near-inertial IGWs project onto larger scales.

>>>>

%
%
%\begin{figure*}[ht]
%  \begin{center}
%    \includegraphics[width=.65\textwidth]{figs/fig5.pdf}
% \caption{\small Surface (horizontal) kinetic energy (a) and sea-surface height variance wavenumber spectra (b)
% in the 1/48$^\circ$ simulation. Solid lines
% are spectra based on hourly snapshots, and dashed lines are spectra based on daily-averaged
% fields.}
% \label{fig5}
% \end{center}
%\end{figure*}
%
%
%Figure \ref{fig5}a depicts the horizontal wavenumber spectra of surface KE in
%April and October. At scales larger than 20 km, the April and October spectra based on hourly
%velocity snapshots (solid lines) are nearly indistinguishable from each other within 95$\%$ confidence level.
%Consistent with the results of
%\citet{rocha_etal2016}, who analyzed a 3-month output of the LLC4320 simulation in Drake Passage,
%there is significant high-frequency variabilty at submesoscales. Daily-averaging
%the velocity field suppresses spatial variability at scales smaller than about 250
%km, both in April and October (compare solid lines against dashed lines in Figure
%\ref{fig5}a). But this suppression is dramatic in October, when the IGWs peak. At scales
%smaller than 100 km, 39$\%$ of the surface KE in April is accounted for by super-inertial
%flows as opposed to 79$\%$ in October. The seasonality of subinertial submesoscale flows
%is strong, consistent
%with the results of \citet{sasaki_etal2014}, which are
%based on daily-averaged velocity fields of a different model without tidal forcing
%(P. Klein, personal communication).
%
%The IGWs project on the sea-surface.
%There is a dramatic difference between the spectra
%based on hourly and daily-averaged sea-surface height in October (Figure \ref{fig5}b): at scales smaller than 100 km, the spectra
%of hourly sea-surface height roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
%sea-surface height roughly follows a $-5$ power-law. At these scales, 33$\%$ of the sea-surface height variance in April is accounted for by super-inertial
%flows as opposed to 83$\%$ in October. Curiously, the out-of-phase seasonal cycle of submesoscale
%turbulence and near-surface submesoscale IGWs conspire to yield weak seasonality
%in the spectra of KE and sea-surface height variance based on hourly fields.
%
%
\section{Discussion and conclusion}
Our work adds to recent modeling \citep[e.g., ][]{sasaki_etal2014}
and observational \citep[e.g., ]{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. In particular, our main finding is that in global simulations with embedded tides the
near-surface submesoscale IGWs in the Kuroshio Extension undergo
a strong seasonal cycle that is out of phase with the seasonal cycle of
submesoscale turbulence. IGW energy and SSH variance are significantly spread across
the submesoscales, likely through mesoscale refraction and dispersion \citep[e.g.,][and references there in]{ponte_klein2015,alford_etal2016}
 and parametric
subharmonic instability \citep[e.g., ][]{mackinnon_winters2005}. In the LLC simultions,
super-inertial IGWs account for most of the surface submesoscale KE and SSH variance;
near-inertial IGWs project onto larger scales.
